---
output:
  word_document: default
  html_document: default
---
Task 3: The quality appears to be okay. the variables are significant and the AIC number is okay too.

Task 4: Being in Virginia and having multiple offenses are more likely to have violated parole. I believe that this is prettty intuitive on the multiple offenses piece, however, the state seems a little confusing.

Task 5: Being in the state of Virginia and having multiple offenses are the most significant variables. Race is also significant, but not as much as the other two variables. The AIC number is lowered here indicating a good model.

Task 6: Parolee 1 has a .44 chance of violating parole. Parolee 2 has a .15 chance of violating parole.

Task 8: The sensitivity of the model is  0.72 and the specificity is 0.85. The accuracy of the training set with the given cutoff is .86. If we incorrectly classify a parolee, we could be sending innocent people back to prison or letting violators go without punishment.

Task 9: A probability threshold of .6 maxizmizes accuracy on the training set.

Task 10:The test set has an accuracy of .95 making it very accurate.



```{r}
#install.packages('ROCR')
options(tidyverse.quiet = TRUE) 
library(tidyverse)
library(MASS)
library(caret)
library(ROCR)
library(leaps) 
library(e1071)

parole <- read.csv("parole.csv")

```

```{r}


parole <- parole %>% mutate(male = as_factor(as.character(male))) %>%
mutate(male = fct_recode(male,
"female" = "0",
"male" = "1")) 

parole <- parole %>% mutate(race = as_factor(as.character(race))) %>%
mutate(race = fct_recode(race,
"other" = "2",
"white" = "1")) 

parole <- parole %>% mutate(state = as_factor(as.character(state))) %>%
mutate(state = fct_recode(state,
"otherstate" = "1",
"Kentucky" = "2",
"Louisiana"= "3",
"Virginia"= "4")) 

parole <- parole %>% mutate(crime = as_factor(as.character(crime))) %>%
mutate(crime = fct_recode(crime,
"othercrime" = "1",
"larceny" = "2",
"drug-related crime" = "3",
"driving-related crime" = "4")) 


parole <- parole %>% mutate(multiple.offenses = as_factor(as.character(multiple.offenses))) %>%
mutate(multiple.offenses = fct_recode(multiple.offenses,
"not_multiple" = "0",
"multiple_offenses" = "1"))

parole <- parole %>% mutate(violator = as_factor(as.character(violator)))%>%
mutate(violator = fct_recode(violator,
"notviolate" = "0",
"violated" = "1"))

```

```{r Task 1}

set.seed(12345)

train.rows <- createDataPartition(y= parole$violator, p= 0.7, list= FALSE)

train <- parole[train.rows,]

test <- parole[-train.rows,]


```

```{r Task 2}

ggplot(parole, aes(x= male ,fill = violator ))+
  geom_bar()+
  theme_bw()

ggplot(parole, aes(x= race, fill = violator ))+
  geom_bar()+
  theme_bw()

ggplot(parole, aes(x= crime ,fill = violator ))+
  geom_bar()+
  theme_bw()

ggplot(parole, aes(x= multiple.offenses ,fill = violator ))+
  geom_bar()+
  theme_bw()

ggplot(parole, aes(x= time.served ,fill = violator ))+
  geom_bar()+
  theme_bw()

ggplot(parole, aes(x= state ,fill = violator ))+
  geom_bar()+
  theme_bw()

ggplot(parole, aes(x= age ,fill = violator ))+
  geom_bar()+
  theme_bw()

ggplot(parole, aes(x= max.sentence ,fill = violator ))+
  geom_bar()+
  theme_bw()

```

```{r Task 3}

mod1 <- glm(violator ~ state, parole, family = "binomial")

summary(mod1)

```

```{r Task 4}

allmod <- glm(violator ~ male + race + age + state + time.served + max.sentence + multiple.offenses + crime, parole, family = 'binomial')

summary(allmod)

emptymod <- glm(violator ~1, parole, family = "binomial")

summary(emptymod)

backmod <- stepAIC(allmod, direction = "backward", trace = TRUE)

summary(backmod)

```

```{r Task 5}

mod4 <- glm(violator ~ state + multiple.offenses + race, train, family = "binomial")

summary(mod4)

```

```{r Task 6}

Parolee1 <- data.frame(state = "Louisiana", race = "white", multiple.offenses = "multiple_offenses")

predict(backmod, Parolee1, type = "response")

Parolee2 <- data.frame(state = "Kentucky", race = "other", multiple.offenses = "not_multiple")

predict(backmod, Parolee2, type = "response")

```

```{r Task 7}

predictions <- predict(backmod, train, type="response")

head(predictions)

ROCRpred <- prediction(predictions, train$violator)

ROCRperf <-performance(ROCRpred, "tpr", "fpr")
plot(ROCRperf, colorize=TRUE, print.cutoffs.at=seq(0,1,by=0.1), text.adj=c(-0.2,1.7))

as.numeric(performance(ROCRpred, "auc")@y.values)

```

```{r Task 8}

opt.cut = function(perf, pred){
    cut.ind = mapply(FUN=function(x, y, p){
        d = (x - 0)^2 + (y-1)^2
        ind = which(d == min(d))
        c(sensitivity = y[[ind]], specificity = 1-x[[ind]], 
            cutoff = p[[ind]])
    }, perf@x.values, perf@y.values, pred@cutoffs)
}
print(opt.cut(ROCRperf, ROCRpred))

t1 <- table(train$violator,predictions >   0.1527550)
t1

(t1[1,1]+t1[2,2])/nrow(train)

```

```{r Task 9}

t1 <- table(train$violator,predictions > 0.5)
t1

(t1[1,1]+t1[2,2])/nrow(train)

t1 <- table(train$violator,predictions > 0.6)
t1

(t1[1,1]+t1[2,2])/nrow(train)


```

```{r}
predictions_test <- predict(backmod, test, type="response")

head(predictions_test)

ROCRpred_test <- prediction(predictions_test, test$violator)

ROCRperf_test <-performance(ROCRpred_test, "tpr", "fpr")
plot(ROCRperf_test, colorize=TRUE, print.cutoffs.at=seq(0,1,by=0.1), text.adj=c(-0.2,1.7))

as.numeric(performance(ROCRpred_test, "auc")@y.values)

opt.cut = function(perf, pred){
    cut.ind = mapply(FUN=function(x, y, p){
        d = (x - 0)^2 + (y-1)^2
        ind = which(d == min(d))
        c(sensitivity = y[[ind]], specificity = 1-x[[ind]], 
            cutoff = p[[ind]])
    }, perf@x.values, perf@y.values, pred@cutoffs)
}
print(opt.cut(ROCRperf, ROCRpred))

t1_test <- table(test$violator,predictions_test >   0.6)
t1_test

(t1_test[1,1]+t1[2,2])/nrow(test)
```

