---
output:
  word_document: default
  html_document: default
---
Task 1: yes, there does appear to be a natural clustering of drivers. It would appear that the longer the distance driven, the higher the speeds.

Task 3: It doesn't appear that the two clusters have any siilairties between them. There is no real point where they overlap.

Task 4: Yes, the general consensus is that 4 clusters is optimal.

Task 6: There is a lot more overapping of the clusters. Because we have different groups to refer to, we can find mroe similarities/differences in our data at a more granular level.

Task 7: Yes, the consensus is 5 or 6 clusters.


```{r}

options(tidyverse.quiet=TRUE)
library("tidyverse")
library("cluster")
library("factoextra")
library("dendextend")

```

```{r}

trucks <- read_csv("trucks.csv")

summary(trucks)

```

```{r Task 1}

ggplot(trucks, aes(x=Distance, y= Speeding))+
  geom_point()

```

```{r Task 2}

trucks2 <- trucks %>% select("Speeding", "Distance")

trucks2 <- as.data.frame(scale(trucks2))

```

```{r Task 3}

set.seed(1234)
clusters1 <- kmeans(trucks2, 2)

fviz_cluster(clusters1, trucks2)

```

```{r Task 4}

set.seed(1234)
fviz_nbclust(trucks2, kmeans, method = "wss") 

set.seed(1234)
fviz_nbclust(trucks2, kmeans, method = "silhouette") 

```

```{r Task 5}

set.seed(1234)
clusters2 <- kmeans(trucks2, 4)

fviz_cluster(clusters2, trucks2)


```

```{r}

wine <- read_csv("wineprice.csv")

wine2 <- wine %>% select("Price", "WinterRain", "AGST", "HarvestRain", "Age")

wine2 <- as.data.frame(scale(wine2))

```

```{r Task 7}


set.seed(1234)
fviz_nbclust(wine2, kmeans, method = "wss") 

set.seed(1234)
fviz_nbclust(wine2, kmeans, method = "silhouette") 

```

```{r Task 8}

set.seed(1234)
clusters3 <- kmeans(wine2, 5)

fviz_cluster(clusters3, wine2)

```

```{r Task 9}

m <- c( "average", "single", "complete", "ward")
names(m) = c( "average", "single", "complete", "ward")

ac <- function(x) {
  agnes(wine2, method = x)$ac
}
map_dbl(m, ac)

hc <- agnes(wine2, method = "ward") 
pltree(hc, cex = 0.6, hang = -1, main = "Agglomerative Dendrogram") 

plot(hc, cex.axis= 0.5) 
rect.hclust(hc, k = 5, border = 2:6) #border selects colors for the boxes

```

```{r Task 10}

hc2 <- diana(wine2)
pltree(hc2, cex = 0.6, hang = -1, main = "Divisive Dendogram")

plot(hc2, cex.axis= 0.5) 
rect.hclust(hc2, k = 5, border = 2:6)

```

